\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-12-10 doc/flexiblesusy-paper.tex
update masses for Table 1 (polem mass precision comparison)
The new CMSSM parameter point was proposed by Peter and reads

Block MINPAR                 # Input parameters
    1   1000                 # m0
    2   1000                 # m12
    3   10                   # TanBeta
    4   1                    # SignMu
    5   -3300                # Azero

taken from \cite{Bednyakov:2002sf} and read

@@

\cite{Baer:2002ek,Skands:2003cj}

@@

about $2\unit{GeV}$ between \code{MediumPrecision} and

@@

increases the gluino mass about $1\unit{\%}$ for this parameter point.

@@

$\unit{0.4\%}$, one can consider calculating them with

@@

    & $128.3\unit{GeV}$ ($2.45\unit{ms}$)
    & $126.3\unit{GeV}$ ($9.53\unit{ms}$) \\

@@

    & $10167\unit{GeV}$ ($0.10\unit{ms}$)
    & $10167\unit{GeV}$ ($0.10\unit{ms}$)
    & $10251\unit{GeV}$ ($0.38\unit{ms}$) \\

@@

    & $2295\unit{GeV}$ ($4.17\unit{ms}$)
    & $2295\unit{GeV}$ ($16.1\unit{ms}$)
    & $2295\unit{GeV}$ ($64.2\unit{ms}$) \\

@@

    & $4181\unit{GeV}$ ($4.17\unit{ms}$)
    & $4174\unit{GeV}$ ($16.1\unit{ms}$)
    & $4174\unit{GeV}$ ($64.2\unit{ms}$) \\

@@

    & $8703\unit{GeV}$ ($2.45\unit{ms}$)
    & $8714\unit{GeV}$ ($14.9\unit{ms}$)
    & $8734\unit{GeV}$ ($58.5\unit{ms}$) \\

@@

    & $10442\unit{GeV}$ ($2.48\unit{ms}$)
    & $10391\unit{GeV}$ ($15.0\unit{ms}$)
    & $10418\unit{GeV}$ ($59.9\unit{ms}$) \\

@@

    & $7913\unit{GeV}$ ($1.94\unit{ms}$)
    & $7909\unit{GeV}$ ($11.2\unit{ms}$)
    & $7909\unit{GeV}$ ($34.1\unit{ms}$) \\

@@

    methods for the CMSSM with $m_0=8\unit{TeV}$, $M_{1/2}=A_0=5\unit{TeV}$,
    $\tan\beta=20$, $\sign\mu=+1$.  In brackets the time used to calculate

@@

>>>>

taken from \cite{Avdeev:1997sz,Bednyakov:2002sf} and read

@@

\cite{Avdeev:1997sz,Baer:2002ek,Skands:2003cj}

@@

about $1.2\unit{GeV}$ between \code{MediumPrecision} and

@@

increases the gluino mass about $0.5\unit{\%}$ for this parameter point.

@@

$\unit{0.3\%}$, one can consider calculating them with

@@

    & $125.3\unit{GeV}$ ($2.40\unit{ms}$)
    & $124.1\unit{GeV}$ ($9.57\unit{ms}$) \\

@@

    & $2218\unit{GeV}$ ($0.12\unit{ms}$)
    & $2218\unit{GeV}$ ($0.12\unit{ms}$)
    & $2231\unit{GeV}$ ($0.40\unit{ms}$) \\

@@

    & $429\unit{GeV}$ ($4.02\unit{ms}$)
    & $429\unit{GeV}$ ($16.4\unit{ms}$)
    & $429\unit{GeV}$ ($48.3\unit{ms}$) \\

@@

    & $1943\unit{GeV}$ ($4.02\unit{ms}$)
    & $1944\unit{GeV}$ ($16.4\unit{ms}$)
    & $1944\unit{GeV}$ ($48.3\unit{ms}$) \\

@@

    & $1055\unit{GeV}$ ($2.50\unit{ms}$)
    & $1081\unit{GeV}$ ($15.1\unit{ms}$)
    & $1085\unit{GeV}$ ($59.1\unit{ms}$) \\

@@

    & $1801\unit{GeV}$ ($2.54\unit{ms}$)
    & $1778\unit{GeV}$ ($15.3\unit{ms}$)
    & $1783\unit{GeV}$ ($59.7\unit{ms}$) \\

@@

    & $1019\unit{GeV}$ ($1.90\unit{ms}$)
    & $1018\unit{GeV}$ ($11.3\unit{ms}$)
    & $1018\unit{GeV}$ ($22.6\unit{ms}$) \\

@@

    methods for the CMSSM with $m_0=M_{1/2}=1\unit{TeV}$, $A_0=-3.3\unit{TeV}$,
    $\tan\beta=10$, $\sign\mu=+1$.  In brackets the time used to calculate

@@

%\cite{Avdeev:1997sz}
\bibitem{Avdeev:1997sz}
  L.~V.~Avdeev and M.~Y.~Kalmykov,
  %``Pole masses of quarks in dimensional reduction,''
  Nucl.\ Phys.\ B {\bf 502} (1997) 419
  [hep-ph/9701308].
  %%CITATION = HEP-PH/9701308;%%
  %66 citations counted in INSPIRE as of 28 Nov 2014
